Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-07-27 main-sketch.tex
paragraph

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[Data set sizing from $300$ to $800$ ]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_800.eps}
    \label{subsubsec_vs_datasize1a}
  }
  \subfigure[Data set sizing from $14000$ to $20000$]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_20000.eps}
  \label{subsubsec_vs_datasize1b}} 
\caption{With $\betad(1,1)$ prior distribution, Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{balanced} datasets
of observations. This means that in the Beta-Binomial setting (Figure \ref{subsubsec_vs_datasize1a},
and \ref{subsubsec_vs_datasize1b}) the datasets will be half 1s and half 0s, while int the
Dirichelet-Multinomial (Figure  \ref{fig_vs_datasize_dir1a} and \ref{fig_vs_datasize_dir1b})
the data will be equally split in all the $k=3$ bins.
The results show that when the data size
increases, the average errors of
$\hexpmech$, $\hexpmechd$, and Laplace decrease. For small datasets,
i.e with size less 650 in the case of Beta-Binomial systems,
the Laplace mechanisms outperforms the exponential mechanisms,
but for bigger datasets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
we considered datasets of the order of 15 thousands elements,
the exponential mechanisms outperforms the Laplacian mechanism.
\paragraph{Increasing dimensions and data size with balanced dataset}
\label{subsubsec_vs_dimension}
In Figure \ref{fig_vs_dimension}, in the x-axis are observed data sets
of different sizes and different dimensions. The plot shows that
increasing the number of dimensions has a similar pejorative effect on
$\hexpmech, \hexpmechd$, and the Laplace mechanism. Fixing the number
of dimensions and increasing the data size shows that the Laplace
mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. In
other words, dimensions have little influence on whether our
mechanisms will beat the Laplace mechanism.

>>>>

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[Data set sizing from $300$ to $800$ ]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_800.eps}
    \label{subsubsec_vs_datasize1a}
  }
  \subfigure[Data set sizing from $14000$ to $20000$]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_20000.eps}
  \label{subsubsec_vs_datasize1b}} 
\caption{With prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[Data set sizing from $300$ to $800$ ]{

    \label{subsubsec_vs_datasize1adir}
  }
  \subfigure[Data set sizing from $14000$ to $20000$]{

  \label{subsubsec_vs_datasize1bdir}} 
\caption{With $\betad(1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_dir}
\end{center}
\end{figure}

In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{unbalanced} datasets
of observations. This means that in the Beta-Binomial setting (Figure \ref{subsubsec_vs_datasize1a},
and \ref{subsubsec_vs_datasize1b}) the datasets will consist of 10\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})
the data will be split in the $k=3$ bins with perecentages of: 20\%, 30\% and 50\%.
The results show that when the data size
increases, the average errors of
$\hexpmech$, $\hexpmechd$, and Laplace decrease. For small datasets,
i.e with size less 650 in the case of Beta-Binomial systems,
the Laplace mechanisms outperforms the exponential mechanisms,
but for bigger datasets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
we considered datasets of the order of 15 thousands elements,
the exponential mechanisms outperforms the Laplacian mechanism.
Similar experimental results were obtainted for the Dirichelet-Multinomial system.
\paragraph{Increasing dimensions and data size with balanced dataset}
\label{subsubsec_vs_dimension}
In Figure \ref{fig_vs_dimension}, in the x-axis are observed data sets
of different sizes and different dimensions. The plot shows that
increasing the number of dimensions has a similar pejorative effect on
$\hexpmech, \hexpmechd$, and the Laplace mechanism. Fixing the number
of dimensions and increasing the data size shows that the Laplace
mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. In
other words, dimensions have little influence on whether our
mechanisms will beat the Laplace mechanism.
